### 2014-11-03 thesis/method/evaluation.tex
Lots of changes

\section{Evaluation Procedure}
\subsection{Steps Involved}
The steps that we took to evaluate the performance of the various classifiers
and feature selection methods were:
\begin{enumerate}
\item The trauma LOS data was cleaned and preprocessed as described in Chapter
\ref{chap:preprocess}, giving us two data sets: one with and one without
discretisation. The general LOS data from Portugal was already cleaned when we
received it; however, we discretised the continuous \texttt{los} variable to
the same categories as for the trauma data (2 days or less, greater than 2
days), normalised the numeric attribute \texttt{prev\_admissions}, and derived
both a discretised and non-discretised data set. This resulted in 4 sets of
data.
\item For each data set, we evaluated the effect of the 4 automatic feature
selection methods on each of the 8 classifiers described in Chapter
\ref{chap:classification}, giving us 32 configurations for each data set, over
4 sets. Evaluation was performed using \textit{ten-fold stratified
cross-validation} (described below).
\item For the two trauma LOS data sets, we additionally evaluated the two
manual feature selection methods with all 8 classifiers. Recall from Section
\ref{sec:manual} that one of the feature sets is from the key previous work
on trauma LOS prediction that we use as a baseline, and the other feature set
is a set of features included through consultation with a domain expert.
\end{enumerate}

@@

\subsubsection{Code Written}
\label{sec:code}
Leading and trailing whitespace was removed and feature names transformed using
code written in Python to manipulate the CSV exported from Microsoft Excel.
All runs of WEKA were executed by
a program we wrote in Bash (a Unix shell) script. This program was able to run
WEKA with the following features:
\begin{itemize}
\item The ability to specify filenames corresponding to the input training data
and the specification of classification or feature selection algorithms to run
\item ROC curve data output can be optionally enabled and saved to disk after
each cross-validation pass
\item An experiment can be repeated an arbitrary number of times -- this is
specified by the user upon invoking the script (default is one time)
\item The ability to specify the inclusion of a random number seed -- this is
necessary for repetitions of runs to generate different cross-validation splits
\item Model information and performance measures are saved to disk after each
cross-validation
\end{itemize}

@@

In order to implement our novel Ranked Distance Nearest Neighbour algorithm,
\ref{sec:rankeddist}), we created our own class within the WEKA Java package
hierarchy. This was implemented in Java and needed to implement the correct
interfaces and override the right inherited methods in order for the $k$-NN
classifier in WEKA to be able to use it as a distance function. This also
involved updating certain properties of the \texttt{weka.jar} executable in
order to use the new class, as well as building the entire WEKA source. The
development environment we used was Eclipse \todo{insert version}, and the
source was built using the 1.7.0 Java runtime.

@@

\begin{figure}[h]
\centering
\includegraphics{images/method/example-roc.eps}
\caption{Two ROC curves on the same graph. Note that the straight line from
the bottom left corner to the top right corner indicates an AUC of 0.5. Curves
which head towards the top left corner indicate increasing AUC.}
\label{fig:sampleroc}
\end{figure}

@@

For each classifier, let the population of all of its accuracy (or AUC)
scores be some random variable $X$, which follows a distribution whose
parameters (such as mean and standard deviation) we do not know.
The Central Limit Theorem from statistics states that given a random
sample of $n$ items from $X$, namely $X_1,X_2,\dots,X_n$, the sample mean
$\bar{x}$
is approximately normally distributed when $n$ is at least roughly around 30
and the $X_i$'s are independent and identically distributed \cite{Phipps2001}.

Consequently, we can construct a $(1-\alpha)$\% normal confidence interval for
$\bar{x}$ -- where $\alpha$ is commonly called the
\textit{significance level} -- as follows \cite{Wasserman2003}:
\begin{equation*}
  \left[\bar{x} - z_{1-\alpha/2}\dfrac{s}{\sqrt{n}},
    \bar{x} + z_{1-\alpha/2}\dfrac{s}{\sqrt{n}}\right]
\end{equation*}
where $\bar{x}$ is the sample mean, $\alpha$ is the significance level
(5\% or $0.05$ in our case), $s$ is the sample standard deviation, $n$
is the number of observations in our sample, and $z_{1-\alpha/2}$ is the value
of the standard normal variable $Z \sim \mathcal{N}(0,1)$ with cumulative
probability $1-\alpha/2$.

These confidence intervals can be constructed

In our work, we repeated the ten-fold stratified cross-validation procedure
ten times, leading to $n=100$ samples with which to obtain our confidence
estimates.

\subsection{Tests for Statistical Significance}
To decide whether or not the difference in values of each measure between
classifiers and feature selection methods was statistically significant,
paired $t$-tests at a significance level of 0.05 were conducted.
\todo{elaborate}

\section{Summary}
In this section we described our method of evaluating the performance of each
classifier and feature selection method that we use. We used accuracy and the
area under the curve to measure two different aspects of our classifiers, and
we obtained these figures using stratified ten-fold cross-validation. Paired
$t$-tests were conducted to test for statistical significance.

>>>>

\section{Evaluation Procedure}
\subsection{Steps Involved}
The steps that we took to evaluate the performance of the various classifiers
and feature selection methods were:
\begin{enumerate}
\item The trauma LOS data was cleaned and preprocessed as described in Chapter
\ref{chap:preprocess}, giving us two data sets: one with and one without
discretisation. The general LOS data from Portugal was already cleaned when we
received it; however, we discretised the continuous \texttt{los} variable to
the same categories as for the trauma data (2 days or less, greater than 2
days), normalised the numeric attribute \texttt{prev\_admissions}, and derived
both a discretised and non-discretised data set. This resulted in 4 sets of
data.
\item For each data set, we evaluated the effect of the 4 automatic feature
selection methods on each of the 11 classifiers described in Chapter
\ref{chap:classification}, giving us 44 configurations for each data set, over
4 sets. Evaluation was performed using \textit{ten-fold stratified
cross-validation} (described below).
\item For the two trauma LOS data sets, we additionally evaluated the two
manual feature selection methods with all 8 classifiers. Recall from Section
\ref{sec:manual} that one of the feature sets is from the key previous work
on trauma LOS prediction that we use as a baseline, and the other feature set
is a set of features included through consultation with a domain expert.
\end{enumerate}

@@

\subsubsection{Code Written}
\label{sec:code}
Leading and trailing whitespace was removed and feature names transformed using
code written in Python (language version 3.4.1) to manipulate the CSV exported
from Microsoft Excel. All runs of WEKA were executed by
a program we wrote in Bash (a Unix shell) script. This program was able to run
WEKA with the following features:
\begin{itemize}
\item The ability to specify filenames corresponding to the input training data
and the specification of classification or feature selection algorithms to run
\item ROC curve data output can be optionally enabled and saved to disk after
each cross-validation pass
\item An experiment can be repeated an arbitrary number of times -- this is
specified by the user upon invoking the script (default is one time)
\item The ability to specify the inclusion of a random number seed -- this is
necessary for repetitions of runs to generate different cross-validation splits
\item Model information and performance measures are saved to disk after each
cross-validation
\end{itemize}

@@

In order to implement our novel Ranked Distance Nearest Neighbour algorithm,
\ref{sec:rankeddist}), we created our own class within the WEKA Java package
hierarchy. This was implemented in Java and needed to implement the correct
interfaces and override the right inherited methods in order for the $k$-NN
classifier in WEKA to be able to use it as a distance function. This also
involved updating certain properties of the \texttt{weka.jar} executable in
order to use the new class, as well as building the entire WEKA source. The
development environment we used was Eclipse 4.2.1, and the
source was built using version 1.7.0 Update 17 of the Java Development Kit.

@@

\begin{figure}[h]
\centering
\includegraphics{images/method/example-roc.eps}
\caption{Three ROC curves on the same graph. Curves
which head towards the top left corner indicate increasing AUC. In this
example, the curve labelled `No feature selection' has the highest AUC.}
\label{fig:sampleroc}
\end{figure}

@@

For each classifier, let the population of all of its accuracy (or AUC)
scores be some random variable $X$, which follows a distribution whose
parameters (such as mean and standard deviation) we do not know.
The Central Limit Theorem from statistics states that given a random
sample of $n$ items from $X$, namely $X_1,X_2,\dots,X_n$, the sample mean
$\bar{x}$
is approximately normally distributed when $n$ is at least approximately 30
and the $X_i$'s are independent and identically distributed \cite{Phipps2001}.

Consequently, we can construct a $(1-\alpha)$\% normal confidence interval for
$\bar{x}$ -- where $\alpha$ is commonly called the
\textit{significance level} -- as follows \cite{Wasserman2003}:
\begin{equation*}
  \left[\bar{x} - z_{1-\alpha/2}\dfrac{s}{\sqrt{n}},\text{ }
    \bar{x} + z_{1-\alpha/2}\dfrac{s}{\sqrt{n}}\right]
\end{equation*}
where $\bar{x}$ is the sample mean, $\alpha$ is the significance level
(5\% or $0.05$ in our case), $s$ is the sample standard deviation, $n$
is the number of observations in our sample, and $z_{1-\alpha/2}$ is the value
of the standard normal variable $Z \sim \mathcal{N}(0,1)$ with cumulative
probability $1-\alpha/2$.

These confidence intervals can be constructed by computing the average and
standard deviation of performance estimates of at least three ten-fold
cross-validation runs per classifier.
In our work, we repeated the ten-fold stratified cross-validation procedure
ten times, leading to $n=100$ samples with which to obtain our confidence
estimates.

\subsection{Tests for Statistical Significance}
We conducted paired $t$-tests in order to determine whether or not our
improvements in performance were statistically significant at the 95\% level.
This is done by comparing the results from ten-fold cross-validation, which
are means. We are also able to take advantage of the paired test because we
can use the same way of creating the cross-validation folds for different
classifiers, giving us a more accurate result.

\section{Summary}
In this section we described our method of evaluating the performance of each
classifier and feature selection method that we use. We used accuracy and the
area under the curve to measure two different aspects of our classifiers, and
we obtained these figures using stratified ten-fold cross-validation. Paired
$t$-tests were conducted to test for statistical significance of improvements
in accuracy and AUC.

### 2014-11-03 thesis/method/preprocess.tex
Lots of changes

\section{Data Sets}
In our work we obtained two independent sets of LOS data, one specifically for
trauma and the other a general, hospital-wide set.

\subsection{Trauma LOS Data}
\subsubsection{Collection}
The data set used consisted of trauma registry data from the trauma centre
at the Royal Prince Alfred Hospital, a major trauma centre in New South Wales,
Australia. It covered all adult (age 15 and over) inpatient admissions to the
trauma centre from 2007--2011.

@@

\subsubsection{Features}

\subsection{General Hospital LOS Data}
By collaborating with our colleagues from the University of Minho in Portugal,
we were able to obtain LOS data for all inpatient hospitalisations from
2000--2013 at the Hospital das Foras Armadas in Lisboa, Portugal. The data
contained 26462 inpatient records spanning all medical departments within the
hospital, comprising 15 features that were not specific to any medical domain.

\subsubsection{Features}

@@

\paragraph{Incorrect spelling and punctuation.}
Since the data was initially in Excel spreadsheet format, we explored the data
by hand using Microsoft Excel's filter on each column. This allowed us to see
the range of possible values for each feature and easily detect anomalous
selling and punctuation:
\begin{itemize}
  \item In the \texttt{sex} attribute, there were values of `Female' and
  `Femal' which were consolidated into `Female'.
  \item In the \texttt{mechanism} attribute, which was textual and indicated
  the category of how the patient was injured, there were such categories as
  `Other Vehi' and `Other Vehicle' as well as `Pedal Cycl' and `Pedal Cyclist'.
  Such categories were combined into `Other Vehicle' and `Pedal Cyclist'
  respectively.
  \item Some categories in \texttt{mechanism} were also divided into whether or
  not the mechanism of injury was self-inflicted, such as `Shooting' and
  `Shooting-selfinflicted'. At the suggestion of a domain expert, we combined
  them into one category: in this case, simply
  `Shooting'; this was done for all the categories in this attribute.
  \item \texttt{disp from ED} indicated the section of the hospital that the
  patient was discharged to. This was also a textual categorical attribute.
  There were redundancies like `G. ICU' and `G.ICU' and even `GICU', which we
  all combined into one category, `GICU'.
\end{itemize}

\paragraph{Extraneous whitespace or other characters.}
After correcting for spelling and punctuation errors,
the data was then exported into CSV (comma-separated value) format, so that
we could continue to process it programmatically rather than manually without
having to use Excel. Many
fields in the data set contained leading or trailing whitespace, which was
removed with a few lines of Python code (see appendix \todo{[add reference
to appendix]}). All attribute names were converted to lowercase. In the case
where attribute names consisted of several words, the spaces were replaced
with underscores (\_) to ensure that the full attribute name was read.
For example, \texttt{Any Cancer} was converted into \texttt{any\_cancer}.

@@

@@

The \textit{minimum description length (MDL)} principle is used to determine
the stopping criterion. The MDL value is calculated by adding the information
values from two cases: split or do not split. If we split, then we can encode
the split point in $\mathrm{log}_2(N-1)$ bits (where $N$ is the number of
instances), then the classes of those above and below it. If we do not split,
then each instance's label must be encoded. Mathematically, given $N$ examples
with entropy $E$, sub-intervals $k_1$ and $k_2$ with the entropy of examples
in each sub-interval denoted $E_1$ and $E_2$:
\begin{equation*}
\mathrm{MDL} = \dfrac{\mathrm{log}_2(N-1)}{N} + \dfrac{\mathrm{log}_2(3^k-2) - kE + k_1E_1 + k_2E_2}{N}
\end{equation*}
The first term is the information needed for the splitting point, and the
second is a correction necessary for encoding which classes belong to which
sub-interval. The decision rule is then to split if the information gain for
that split exceeds the MDL value: $\mathrm{gain} > \mathrm{MDL}$.

@@

The data was discretised according to the above method using the supervised
discretisation filter in WEKA. We keep both the original data set (without
discretisation) and the discretised data set for comparison.

>>>>

\section{Data Sets}
In our work we obtained two independent sets of LOS data, one specifically for
trauma and the other a general, hospital-wide data set.

\subsection{Trauma}
\subsubsection{Collection}
The data set used consisted of trauma registry data from the trauma centre
at the Royal Prince Alfred Hospital, a major trauma centre in New South Wales,
Australia. It covered all adult (age 15 and over) inpatient admissions to the
trauma centre from 2007--2011.

@@

\subsubsection{Features}
The features present in the original data set are listed and briefly described
in Table \ref{tab:feature-desc-tr}.

\subsection{General Hospital}
By collaborating with our colleagues from the University of Minho in Portugal,
we were able to obtain LOS data for all inpatient hospitalisations from
2000--2013 at the Hospital das Foras Armadas in Lisboa, Portugal. The data
contained 17547 inpatient records spanning all medical departments within the
hospital, comprising 15 features that were not specific to any medical domain.
One of these features was the class, \texttt{LOS48}, indicating a stay of
less than or equal to 2 days.

\subsubsection{Features}
The features present in the original data set are listed and briefly described
in Table \ref{tab:feature-desc-pt}.

\input{method/feature-descriptions.tex}

@@

\subsection{Trauma Data}
\paragraph{Incorrect spelling and punctuation.}
Since the data was initially in Excel spreadsheet format, we explored the data
by hand using Microsoft Excel's filter on each column. This allowed us to see
the range of possible values for each feature and easily detect anomalous
selling and punctuation:
\begin{itemize}
  \item In the \texttt{sex} attribute, there were values of `Female' and
  `Femal' which were consolidated into `Female'.
  \item In the \texttt{mechanism} attribute, which was textual and indicated
  the category of how the patient was injured, there were such categories as
  `Other Vehi' and `Other Vehicle' as well as `Pedal Cycl' and `Pedal Cyclist'.
  Such categories were combined into `Other Vehicle' and `Pedal Cyclist'
  respectively.
  \item Some categories in \texttt{mechanism} were also divided into whether or
  not the mechanism of injury was self-inflicted, such as `Shooting' and
  `Shooting-selfinflicted'. At the suggestion of a domain expert, we combined
  them into one category: in this case, simply
  `Shooting'; this was done for all the categories in this attribute.
  \item \texttt{disp from ED} indicated the section of the hospital that the
  patient was discharged to. This was also a textual categorical attribute.
  There were redundancies like `G. ICU' and `G.ICU' and even `GICU', which we
  all combined into one category, `GICU'.
\end{itemize}

\paragraph{Extraneous whitespace or other characters.}
After correcting for spelling and punctuation errors,
the data was then exported into CSV (comma-separated value) format, so that
we could continue to process it programmatically rather than manually without
having to use Excel. Many
fields in the data set contained leading or trailing whitespace, which was
removed with a few lines of Python code (see Appendix
\ref{sec:python-preprocess}).
All attribute names were converted to lowercase. In the case
where attribute names consisted of several words, the spaces were replaced
with underscores (\_) to ensure that the full attribute name was read.
For example, \texttt{Any Cancer} was converted into \texttt{any\_cancer}.

@@

\subsection{General Hospital Data}
The general hospital data we received had already been preprocessed. The only
preprocessing here was to
undo the logarithm transform that had been applied to the \texttt{Previous
Admissions} feature.

@@

The \textit{minimum description length (MDL)} principle is used to determine
the stopping criterion. The MDL value is calculated by adding the information
values from two cases: split or do not split. If we split, then we can encode
the split point in $\mathrm{log}_2(N-1)$ bits (where $N$ is the number of
instances), then the classes of those above and below it. If we do not split,
then each instance's label must be encoded. Mathematically, given $N$ examples
with entropy $E$, sub-intervals $k_1$ and $k_2$ with the entropy of examples
in each sub-interval denoted $E_1$ and $E_2$:
\begin{equation*}
\mathrm{MDL} = \dfrac{\mathrm{log}_2(N-1)}{N} + \dfrac{\mathrm{log}_2(3^k-2) - kE + k_1E_1 + k_2E_2}{N}
\end{equation*}
The first term is the information needed for the splitting point, and the
second is a correction necessary for encoding which classes belong to which
sub-interval. The decision rule is then to split if the information gain for
that split exceeds the MDL value.

@@

The data was discretised according to the above method using the supervised
discretisation filter in WEKA. We kept both the original data set (without
discretisation) and the discretised data set for comparison.

### 2014-11-03 thesis/method/selection.tex
Add filter vs wrapper diagram
Fix strange scaling of SVM, MLP and feature selection diagrams
A whole bunch of updates including source code listing in the appendix
Lots of changes

To evaluate the ``goodness'' of a subset of features with the class $C$, we
compute:
\begin{equation}
\label{eqn:cfs}
\dfrac{\sum_j U(A_j,C)}{\sqrt{\sum_i \sum_j U(A_i,A_j)}}
\end{equation}
where $i$ and $j$ range over the features in the subset being evaluated. The
maximum value that Equation \ref{eqn:cfs} can obtain is 1 when all features
correlate perfectly with the class and also with each other -- the numerator
becomes $n$ and the denominator $\sqrt{n^2}$ if the subset has $n$ features.
\todo{elaborate a bit more}

@@

A higher value for $r_i$ indicates higher correlation with the class. We
rank all features according to their $r_i$ from highest to lowest, and select
some subset of these either by selecting a fixed number, or selecting all
features that have a correlation above a specified threshold.

@@

We can compute the IG for each feature and then select subsets of features that
are greater than some threshold we specify.

@@

We can also select a fixed number of features or all features above a certain
1R accuracy threshold.

@@

\begin{figure}[h]
\caption{Filter and wrapper approaches to feature selection. Note the role of
the learning algorithm in the wrapper method.}
\label{fig:wrapper}
\centering
%\includegraphics[scale=0.95]{images/a2-nn}
\end{figure}

A key advantage of the wrapper approach is that the selected feature sets are
specifically tailored to a learning algorithm, which ensures the best
performance of that algorithm given the data set. However, wrapper approaches
can also be prohibitively slow if the data or feature sets are large and the
chosen learning algorithm expensive to train (such as support vector machines
and multi-layer perceptrons). We will evaluate the use of C4.5 decision trees
(see Section \ref{sec:c45}) in selecting features using the wrapper approach.
Using decision trees to select features is relatively fast as due to the
divide and conquer nature of the learning algorithm, and the tendency of the
trees to select fewer features for learning than other algorithms.

>>>>

To evaluate the ``goodness'' or \textit{merit} of a subset of features with
the class $C$, we compute:
\begin{equation}
\label{eqn:cfs}
\dfrac{\sum_j U(A_j,C)}{\sqrt{\sum_i \sum_j U(A_i,A_j)}}
\end{equation}
where $i$ and $j$ range over the features in the subset being evaluated. The
maximum value that Equation \ref{eqn:cfs} can obtain is 1 when all features
correlate perfectly with the class and also with each other -- the numerator
becomes $n$ and the denominator $\sqrt{n^2}$ if the subset has $n$ features.

CFS conducts a search through subsets of all features in order to find the
one feature subset that has the best merit.

@@

A higher value for $r_i$ indicates higher correlation with the class. We
rank all features according to their $r_i$ from highest to lowest, and select
some subset of these either by selecting a fixed number, or selecting all
features that have a correlation above a specified threshold. We start with a
threshold of 0 and gradually increase this by larger amounts. This is because
a large number of features are usually discarded in the lower thresholds, and
we would like to investigate a range of resulting subset sizes.

@@

We can compute the IG for each feature and then select subsets of features that
are greater than some threshold we specify, similarly to the correlation
coefficient method of feature selection. We choose a similar set of thresholds
because of the high numbers of features with very low information gain.

@@

We can also select a fixed number of features or all features above a certain
1R accuracy threshold. This threshold is a slightly different quantity to the
threshold of the correlation coefficient and information gain methods, as it
is an accuracy, expressed in percentages. Our first threshold is the Zero-R
accuracy for the trauma data set, which is the lower of the two Zero-R
accuracies on our two data sets. We increase this percentage by in increasing
increments to obtain a range of thresholds up to nearly 97\% accuracy (which
discards all features for both data sets). Using the same thresholds across
both data sets allows us to make valid comparisons of the effect of feature
selection on performance.

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.9]{images/method/feature-selection.pdf}
\caption{Filter and wrapper approaches to feature selection. Note the role of
the learning algorithm in the wrapper method.}
\label{fig:wrapper}
\end{figure}

A key advantage of the wrapper approach is that the selected feature sets are
specifically tailored to a learning algorithm, which ensures the best
performance of that algorithm given the data set. However, wrapper approaches
can also be prohibitively slow if the data or feature sets are large and the
chosen learning algorithm expensive to train (such as support vector machines
and multi-layer perceptrons). We will evaluate the use of C4.5 decision trees
(see Section \ref{sec:c45}) in selecting features using the wrapper approach.
Using decision trees to select features is relatively fast as due to the
divide and conquer nature of the learning algorithm, and the tendency of the
trees to select fewer features for learning than other algorithms. Like CFS,
wrapper methods search for the best subset of features and do not require a
threshold to discard attributes.

### 2014-11-03 thesis/results/features-pt-acc.tex
Lots of changes

\begin{tabular}{|l|cccccc|}

@@

 Not discretised & 98.16 & 96.45 & 97.35 & \textit{\begin{tabular}[c]{@{}c@{}}98.22\\ t=0.05\end{tabular}} & \textit{\begin{tabular}[c]{@{}c@{}}98.22\\ t=0.01\end{tabular}} & \begin{tabular}[c]{@{}c@{}}98.16\\ t=74.405\end{tabular} \\ \hline

>>>>

\begin{tabular}{l|cccccc}

@@

 Not discretised & 98.16 & 96.45 & 97.35 & \textit{\begin{tabular}[c]{@{}c@{}}98.22\\ t=0.05\end{tabular}} & \textit{\begin{tabular}[c]{@{}c@{}}98.22\\ t=0.01\end{tabular}} & \begin{tabular}[c]{@{}c@{}}98.16\\ t=74.405\end{tabular} \\

### 2014-11-03 thesis/results/features-pt-auc.tex
Lots of changes

\begin{tabular}{|l|cccccc|}
 \hline

@@

 Not discretised & 0.99 & \textbf{0.983} & \textbf{0.992} & \textit{\begin{tabular}[c]{@{}c@{}}0.993\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.991\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.990\\ t=76.905\end{tabular} \\ \hline

>>>>

\begin{tabular}{l|cccccc}

@@

 Not discretised & 0.99 & \textbf{0.983} & \textbf{0.992} & \textit{\begin{tabular}[c]{@{}c@{}}0.993\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.991\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.990\\ t=76.905\end{tabular} \\

### 2014-11-03 thesis/results/features-tr-acc.tex
Lots of changes

\begin{tabular}{|l|cccccccc|}
\hline

@@

Not discretised & 71.87 & 73.03 & 72.31 & 73.04 & 73.35 & \textit{\begin{tabular}[c]{@{}c@{}}74.65\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}72.63\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}70.99\\ t=66.905\end{tabular} \\ \hline

>>>>

\begin{tabular}{l|cccccccc}

@@

Not discretised & 71.87 & 73.03 & 72.31 & 73.04 & 73.35 & \textit{\begin{tabular}[c]{@{}c@{}}74.65\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}72.63\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}70.99\\ t=66.905\end{tabular} \\

### 2014-11-03 thesis/results/features-tr-auc.tex
Lots of changes

Not discretised & 0.78 & 0.781 & 0.774 & 0.799 & 0.804 & \textit{\begin{tabular}[c]{@{}c@{}}0.818\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.788\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.752\\ t=68.905\end{tabular} \\ \hline

>>>>

Not discretised & 0.78 & 0.781 & 0.774 & 0.799 & 0.804 & \textit{\begin{tabular}[c]{@{}c@{}}0.818\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.788\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.752\\ t=68.905\end{tabular} \\

### 2014-11-03 thesis/results/overall-portugal-acc.tex
Fix broken table and figure labels in latex
Lots of changes

\begin{table}[htbp]
\label{tab:overall-pt-acc}
\caption{Overall best accuracy of each classifier with a particular feature selection method on the general hospital data set. * indicates that results were identical regardless of discretisation. D indicates that discretisation was used, and $t$ is the threshold at which the feature selector was applied. The absence of * or D means that not discretising produced a better result. The best result for each classifier is highlighted in bold, with ties broken in favour of the smallest feature set.}
\begin{tabular}{|l|cccccc|}
\hline
Classifier & None & CFS & C4.5 Wrapper & Correlation & IG & 1R \\ \hline
ZeroR & 75.64* & 75.64* & 75.64* & 75.64* & 75.64* & 75.64* \\
1R & 92.88* & 92.88* & 92.88* & 92.88* & 92.88* & 92.88* \\
NB & 93.66* & 93.06* & 93* & \textbf{\begin{tabular}[c]{@{}c@{}}93.72*\\ t=0.125\end{tabular}} & \begin{tabular}[c]{@{}c@{}}93.66*\\ t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}93.66*\\ t=74.405\end{tabular} \\
DT & \textbf{98.23*} & 96.45* & 97.43* & \begin{tabular}[c]{@{}c@{}}98.23\\ t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.23\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.23\\ t=74.405\end{tabular} \\
LR & \textbf{97.93*} & 96.46* & 97.19* & \begin{tabular}[c]{@{}c@{}}97.93\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}97.93\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}97.93\\ t=74.405\end{tabular} \\
SVM & \textbf{98.01*} & 96.46* & 97.14* & \begin{tabular}[c]{@{}c@{}}98.01\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.01\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.01\\ t=74.405\end{tabular} \\
1NN & \begin{tabular}[c]{@{}c@{}}96.93\\ D\end{tabular} & 96.45* & 97.36* & \textbf{\begin{tabular}[c]{@{}c@{}}97.59*\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}97.57*\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}97.43*\\ t=76.905\end{tabular} \\
20NN & 96.85 & 96.24* & 97.15* & \textbf{\begin{tabular}[c]{@{}c@{}}97.3\\ T=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}97.15\\ T=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}96.86\\ T=68.905\end{tabular} \\
RD & 97.34 & 79.1* & 95.45* & \begin{tabular}[c]{@{}c@{}}97.3\\ t=0\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}97.36\\ t=0\end{tabular}} & \begin{tabular}[c]{@{}c@{}}97.34\\ t=68.905\end{tabular} \\
K* & 97.36 & 92.94* & 96.53* & \textbf{\begin{tabular}[c]{@{}c@{}}97.46*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}97.46*\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}97.36\\ t=74.405\end{tabular} \\
MLP & 98.16 & 96.45* & 97.35* & \textbf{\begin{tabular}[c]{@{}c@{}}98.22*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}98.22*\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.16\\ t=74.405\end{tabular} \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[htbp]
\begin{tabular}{l|cccccc}
Classifier & None & CFS & C4.5 Wrapper & Correlation & IG & 1R \\ \hline
ZeroR & 75.64* & 75.64* & 75.64* & 75.64* & 75.64* & 75.64* \\
1R & 92.88* & 92.88* & 92.88* & 92.88* & 92.88* & 92.88* \\
NB & 93.66* & 93.06* & 93* & \textbf{\begin{tabular}[c]{@{}c@{}}93.72*\\ t=0.125\end{tabular}} & \begin{tabular}[c]{@{}c@{}}93.66*\\ t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}93.66*\\ t=74.405\end{tabular} \\
DT & \textbf{98.23*} & 96.45* & 97.43* & \begin{tabular}[c]{@{}c@{}}98.23\\ t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.23\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.23\\ t=74.405\end{tabular} \\
LR & \textbf{97.93*} & 96.46* & 97.19* & \begin{tabular}[c]{@{}c@{}}97.93\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}97.93\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}97.93\\ t=74.405\end{tabular} \\
SVM & \textbf{98.01*} & 96.46* & 97.14* & \begin{tabular}[c]{@{}c@{}}98.01\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.01\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.01\\ t=74.405\end{tabular} \\
1NN & \begin{tabular}[c]{@{}c@{}}96.93\\ D\end{tabular} & 96.45* & 97.36* & \textbf{\begin{tabular}[c]{@{}c@{}}97.59*\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}97.57*\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}97.43*\\ t=76.905\end{tabular} \\
20NN & 96.85 & 96.24* & 97.15* & \textbf{\begin{tabular}[c]{@{}c@{}}97.3\\ T=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}97.15\\ T=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}96.86\\ T=68.905\end{tabular} \\
RD & 97.34 & 79.1* & 95.45* & \begin{tabular}[c]{@{}c@{}}97.3\\ t=0\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}97.36\\ t=0\end{tabular}} & \begin{tabular}[c]{@{}c@{}}97.34\\ t=68.905\end{tabular} \\
K* & 97.36 & 92.94* & 96.53* & \textbf{\begin{tabular}[c]{@{}c@{}}97.46*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}97.46*\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}97.36\\ t=74.405\end{tabular} \\
MLP & 98.16 & 96.45* & 97.35* & \textbf{\begin{tabular}[c]{@{}c@{}}98.22*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}98.22*\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}98.16\\ t=74.405\end{tabular} \\
\end{tabular}
\caption{Overall best accuracy of each classifier with a particular feature selection method on the general hospital data set. * indicates that results were identical regardless of discretisation. D indicates that discretisation was used, and $t$ is the threshold at which the feature selector was applied. The absence of * or D means that not discretising produced a better result. The best result for each classifier is highlighted in bold, with ties broken in favour of the smallest feature set.}
\label{tab:overall-pt-acc}
\end{table}
